---
title: "Meta_Analysis_"
author: "Juan Balcazar"
date: "5/30/2023"
output: html_document
---

```{r setup, include=FALSE}
library(esc)
library(meta)
library(metafor)
library(dmetar)
library(data.table)

```
#install dmetar here: devtools::install_github("MathiasHarrer/dmetar")

# Calculated Hedge's g given certain statistics
## FOR WHEN studies only report certain statistics and you want to include them
#the ESC library helps us convert any weird study to Hedge's g
#One-way anova
We can also derive the SMD from the F-value of a one-way ANOVA with two groups. Such ANOVAs can be identified by looking at the degrees of freedom. In a one-way ANOVA with TWO groups, the degrees of freedom should always start with 1 (e.g. F1,147=5.31).

```{r Convert to G, given F-value (2 groups), include=FALSE}
library(esc)
esc_f(f = 6.95,      # F value of the one-way anova (2 groups)
      grp1n = 26,   # sample size of group 1 (which is "experimental" does not matter in this calculation) 
      grp2n = 47,   # sample size of group 2
      es.type = "g") # convert to Hedges' g; use "d" for SMD

```

#given. Means and SDs. First get the standard error
```{r Convert to G, given means, standard error, include=FALSE}
library(esc)
# Compute the standard error first: standard error= standard deviation divided by the sqrt of sample size 
#at https://www.allmath.com/standard-error-calculator.php


esc_mean_se(grp1n = 24,    # sample in group 1
            grp1m = 35.94,   # mean of group 1,exp
            grp1se = 0.54705,  # standard error of group 1
            
            grp2n = 39,    # sample in group 2
            grp2m = 34.98,    # mean of group 2
            grp2se = 0.32186,  # standard error of group 2
          
            es.type = "g") # use "g" for Hedges' g
```

#given p-value and Cohen's D, we can calculate both the SE and hedges G
```{r GIVEN p-value and Cohen's d, include=FALSE}
se.from.p(0.1,
          p = 0.707,
          N = 189,
          effect.size.type = "difference",
           calculate.g=TRUE)
```


```{r Convert to G, given a t-test}
esc_t(t = 4.03,     # t-value 
      grp1n = 41, # sample size of group1 ('which is experimental and which is control won't matter)
      grp2n = 44, # sample size of group 2
      es.type="g") # convert to SMD; use "g" for Hedges' g
```

#Independent two-sample t-test
```{r Convert to G, given indp. two-sample, include=FALSE}
esc_t(t = 6.86,     # t-value 
      grp1n = 27, # sample size of group1
      grp2n = 27, # sample size of group 2
      es.type="g") # convert to SMD; use "g" for Hedges' g

```

#Inputs: pre-calculated Hedges'g (format: csv)
#explanation: We inputHedge's g data we just calculated into a CSV and feed that 
into our meta-gen object. 
```{r  Input, include=FALSE}
#takes any 
library(data.table)

#load data
AnxietyDecis <- fread (file = "/Users/juanbalcazar/Downloads/PreCal_HedgesG_Meta - Anxiety and Decison-making(2).csv")

AnxietyFlex <- fread(file = "/Users/juanbalcazar/Downloads/PreCal_HedgesG_Meta - Anxiety and Cognitive Flexiblity(1).csv")

DepressDecis <- fread(file = "/Users/juanbalcazar/Downloads/PreCal_HedgesG_Meta - Depression and Decision-making.csv")

DepressFlex <- fread(file = "/Users/juanbalcazar/Downloads/PreCal_HedgesG_Meta - Depression and Cognitive Flexibility.csv")

Subgroup_Flex <- fread(file = "/Users/juanbalcazar/Downloads/PreCal_HedgesG_Meta - Subgroup- Flexibility.csv")

Subgroup_Decis <- fread(file = "/Users/juanbalcazar/Downloads/PreCal_HedgesG_Meta - Subgroup- Decision-making.csv")
```


```{r  Calculation: Calculate Pooled Hedges g pre-calculated Hedges G, include=FALSE}
## Anxiety and decision-making
m.gen <- metagen(TE = TE,
                 seTE = seTE,
                 studlab = Author,
                 data = AnxietyDecis,
                 sm = "SMD", #label (the effect sizes are already SMD, but we can give it a a label)
                 random = TRUE, #random effects model
                 fixed = FALSE,
                 method.tau = "REML", #best for continuous outcomes
                 method.random.ci = "HK", # Knapp-Hartung adjustment: reduce the risk of a false positive result.
                 title = "Anxiety and Decision-making")
m.gen <- update(m.gen, prediction = TRUE)
m.gen

# find outliers
Outliers_Anxiety_Dec<-
find.outliers(m.gen)
Outliers_Anxiety_Dec
```


```{r  Calculation: Calculate Pooled Hedges g pre-calculated Hedges G, include=FALSE}
#Anxiety-CogFlex
m.gen_anxFlex <- metagen(TE = TE,
                 seTE = seTE,
                 studlab = Author,
                 data = AnxietyFlex,
                 sm = "SMD", #label (the effect sizes are already SMD, but we can give it a a label)
                 random = TRUE, #random effects model
                 fixed = FALSE,
                 method.tau = "REML", #best for continuous outccomes
                 method.random.ci = "HK", # Knapp-Hartung adjustment: reduce the risk of a false positive result.
                 title = "Anxiety and Flexibility")

m.gen_anxFlex  <- update(m.gen_anxFlex, prediction = TRUE)
m.gen_anxFlex
```


```{r  Calculation: Calculate Pooled Hedges g pre-calculated Hedges G, include=FALSE}
#depression-cogFlex
m.gen_depressFlex <- metagen(TE = TE,
                 seTE = seTE,
                 studlab = Author,
                 data = DepressFlex,
                 sm = "SMD", #label (the effect sizes are already SMD, but we can give it a a label)
                 random = TRUE, #random effects model
                 fixed = FALSE,
                 method.tau = "REML", #best for continuous outccomes
                 method.random.ci = "HK", # Knapp-Hartung adjustment: reduce the risk of a false positive result.
                 title = "Depression and Flexibility")

m.gen_depressFlex <- update(m.gen_depressFlex, prediction = TRUE)
m.gen_depressFlex

# find outliers
Outliers_DepressFlex<-
find.outliers(m.gen_depressFlex)
Outliers_DepressFlex
```


```{r  Calculation: Calculate Pooled Hedges g pre-calculated Hedges G, include=FALSE}
#depression-decision
m.gen_depressDecis <- metagen(TE = TE,
                 seTE = seTE,
                 studlab = Author,
                 data = DepressDecis,
                 sm = "SMD", #label (the effect sizes are already SMD, but we can give it a a label)
                 random = TRUE, #random effects model
                 fixed = FALSE,
                 method.tau = "REML", #best for continuous outccomes
                 method.random.ci = "HK", # Knapp-Hartung adjustment: reduce the risk of a false positive result.
                 title = "Depression and Decision-making")

m.gen_depressDecis  <- update(m.gen_depressDecis, prediction = TRUE)
m.gen_depressDecis


# find outliers
Outliers_DepressDecis<-
find.outliers(m.gen_depressDecis)
Outliers_DepressDecis
```

Compare the pooled effects, using apriori fixed effects (anxiety, depression)

```{r  Subgroup Analysis, include=FALSE}
#subgroup-Flexibility
subgroupFlex <- metagen(TE = TE,
                 seTE = seTE,
                 studlab = Author,
                 data = Subgroup_Flex,
                 sm = "SMD", #label (the effect sizes are already SMD, but we can give it a a label)
                 random = TRUE, #random effects model
                 fixed = FALSE,
                 subgroup = Subgroup,
                 method.tau = "REML", #best for continuous outccomes
                 method.random.ci = "HK", # Knapp-Hartung adjustment: reduce the risk of a false positive result.
                 title = "Subgroup Analysis, Flexibility")
subgroupFlex

#subgroup-decison-making
subgroupDecis<- metagen(TE = TE,
                 seTE = seTE,
                 studlab = Author,
                 data = Subgroup_Decis,
                 sm = "SMD", #label (the effect sizes are already SMD, but we can give it a a label)
                 random = TRUE, #random effects model
                 fixed = FALSE,
                 subgroup = Subgroup,
                 method.tau = "REML", #best for continuous outccomes
                 method.random.ci = "HK", # Knapp-Hartung adjustment: reduce the risk of a false positive result.
                 title = "Subgroup Analysis, Decision-making")
subgroupDecis
```


Create Forest plots from each metagen object
```{r FOREST, include=FALSE}
plotAnxietyDec <-
meta::forest(m.gen, 
             sortvar = TE,
             
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

plotAnxietyFlex <-
meta::forest(m.gen_anxFlex, 
             sortvar = TE,
             
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

plotDepresFlex <-
  meta::forest(m.gen_depressFlex, 
             sortvar = TE,
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))


```


